A young cluster in the Galactic halo: \\ Recent star formation associated with the Magellanic stream

### 2018-05-18 ms.tex
Add Vasily / Sergey

@@

We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) cross-matched to the \pans\ data release 1 photometry ($griz$ magnitudes; \citealt{Chambers:2016}) to search for distant, comoving multiplets of blue stars.\footnote{We use the cross-match provided by the \gaia\ science archive at \url{https://gea.esac.esa.int/archive/}.}
In detail, we initially query all stars from the \gaia--\pans\ cross-match that have $(g - i) < 1$, parallax $\varpi < 1~{\rm mas}$, and Galactic latitude $|b| > 10^\circ$.

>>>>

\author{Sergey E. Koposov}
\affiliation{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

\author{Vasily Belokurov}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA}

@@

We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) cross-matched to the \pans\ data release 1 photometry ($griz$ magnitudes; \citealt{Chambers:2016}) to search for distant, comoving multiplets of blue stars.\footnote{We use the cross-match provided by the \gaia\ science archive at \url{https://gea.esac.esa.int/archive/}.}
We initially query all stars from the \gaia--\pans\ cross-match that have $(g - i) < 1$, parallax $\varpi < 1~\textrm{mas}$, and Galactic latitude $|b| > 10^\circ$.
